---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dcdcr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

dcdcr contains utilities to work with DataCamp Data Connector. 

This package is designed to be used by administrators and managers of DataCamp groups. Some prior experience of writing reports with R is recommended.

## Installation

You can install the development version with:

``` r
# install.packages("remotes")
remotes::install_github("datacamp/dcdcr")
```
## Before you begin

You need to enable Data Connector in your DataCamp group, and set S3 credentials as environment variables, as described in [this Support article](https://support.datacamp.com/hc/en-us/articles/4405070893591-DataCamp-Data-Connector-A-Step-by-Step-Configuration-Guide-for-Automated-Data-Exports). If in doubt, speak to your Customer Success Manager.

## Importing data

Importing data requires two commands. First you set up the connector to S3, then you get the datasets. By default, all the data is returned for the most recent date.

```{r import}
library(dcdcr)
# Setup connector to Amazon S3
s3_conn <- create_s3_connector()

# Retrieve all data on the latest date available
dc <- get_dc_datasets(s3_conn)

# See the results
str(dc, 1, give.attr = FALSE)
```

You can specify which datasets are returned, on which date.

```{r, team_only}
dc_team <- get_dc_datasets(s3_conn, "team_dim", Sys.Date() - 7)
dc_team
```


