---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE, include = FALSE}
library(dcdcr)
library(dplyr)
```

Here are the currently available content types in the data model for which you can analyze your user progression on a daily basis (daily XP gained and time spent):

- __Course__: A DataCamp course, e.g., Introduction to Python
- __Chapter__: A chapter from a course, e.g., Grouping and Summarizing from the course Introduction to the Tidyverse
- __Exercise__: An exercise from a chapter. Please note that a video is also considered as an exercise (and provides the users with XPs), e.g., Numerical EDA from the chapter Preparation, Exploration, and Visualization from the course Data Science for Everyone
- __Project__: A guided or unguided project, e.g., Exploring the History of Lego
- __Practice__: A practice users can take (on Mobile or in the browser), e.g., Joining Data with dplyr
Assessment: A Signal Assessment, e.g, Statistics Fundamentals with R

For a specific group, the fact tables contain rows for which users worked on content (e.g., exercise, assessment) while they were in this considered group. For example, imagine the following scenario:

Group ID: 1234

- January 1, 2021: User A joins group 1234
- January 2, 2021: User A starts working on a course X
- January 3, 2021: User A leaves group 1234 AND continues working on course X
- January 4, 2021: User A joins group 1234
- January 5, 2021: User A completed course X

In this case, the fact tables for group 1234 and user A will contain rows for the following dates: January 2, 5, and won’t show data for January 3 (even though the user continued working on the course).

Joining the fact tables to the dimension tables allows you to retrieve descriptive information about the content your users worked on (e.g., course title, course topic, maximum XP a user can gain by completing a specific chapter, ...).

```{r echo = FALSE}
docs_bic <- dcdcr:::docs_bic %>% 
  group_by(table_name, table_description) %>% 
  tidyr::nest(columns = c(column, description))



display_doc <- function(.table_name){
  doc <- docs_bic %>% 
    filter(table_name == .table_name)
  cat(glue::glue('## {snakecase::to_title_case(doc$table_name)}\n'))
  cat('\n', doc$table_description, "\n")
  cat('\n### Columns\n')
  doc %>% 
    pull(columns) %>% 
    magrittr::extract2(1) %>% 
    knitr::kable() %>% 
    print()
}
```


```{r results='asis', echo = FALSE}
.table_name <- 'exercise_dim'
docs_bic %>% 
  filter(table_name != 'docs') %>% 
  arrange(table_name) %>% 
  pull(table_name) %>% 
  purrr::walk(display_doc)
```

